Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-03-04 analysis/paper/paper.Rmd
Adding in a schematic diagram for the landmarks
Update to results section, moved the biplots and their descriptive text around

@@

```{r cortex-biplot, fig.cap="PCA biplot for flake shape and dorsal cortex class."}

@@

```{r excavation-unit-biplot, fig.cap="PCA biplot for flake shape and excavation unit."}
# Excavation unit PCA
# ggplot2-based plot of the PCA results using a factoextra function
excavation_unit_biplot <- fviz_pca_ind(pca.geo,
             geom.ind = "point", # show points without labels
            #  line below sets the grouping column for colouring the points
             habillage = as.factor(ma_flakes_tr_with_groups$Unit),
             palette = viridis::cividis(13), # color palette, adjust to preferences
             addEllipses = T, #adds ellipses or convex hulls
             ellipse.type = "convex", #convex hulls
             mean.point = F, #don’t show average point
             legend.title = "Excavation\nunit",
             title = "Change over time in flake shape") +  #adjust accordingly)
             coord_fixed(ratio = 1)  + #adjustable for variation-weighted plots
             theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
              plot.background = element_rect(fill='white',
                                       colour = "white")) +
    theme(plot.title = element_blank())
```

@@

```{r mass-biplot, fig.cap="PCA biplot for flake shape and mass cluster groups"}

@@

In figure \@ref(fig:mass-biplot) we see that greater shape variation is found in the lightest mass classes. The two lightest mass clusters, one and two, are in purple and blue respectively. These first two mass classes span the largest area on the biplot, signifying a larger degree of variation overall.

```{r}
library(cowplot)

plot_grid(
  cortex_biplot, NULL, NULL,  excavation_unit_biplot,  mass_biplot, NULL,
  ncol = 2,
  labels = c("A", NULL, NULL,"B","C",NULL),
  label_size = 12,
  align = "v",
  rel_heights = c(1.1,
                  1,
                  1.1,
                  4,
                  1,
                  1),
  rel_widths = c(2,
                 2,
                 2,
                 4,
                 2,
                 1))

@@

>>>>

![This is a test.](./test_graphic.png)

@@

```{r, fig.cap="PCA biplot for flake shape and dorsal cortex class."}

@@

```{r, fig.cap="PCA biplot for flake shape and excavation unit."}
# Excavation unit PCA
# ggplot2-based plot of the PCA results using a factoextra function
excavation_unit_biplot <- fviz_pca_ind(pca.geo,
             geom.ind = "point", # show points without labels
            #  line below sets the grouping column for colouring the points
             habillage = as.factor(ma_flakes_tr_with_groups$Unit),
             palette = viridis::cividis(13), # color palette, adjust to preferences
             addEllipses = T, #adds ellipses or convex hulls
             ellipse.type = "convex", #convex hulls
             mean.point = F, #don’t show average point
             legend.title = "Excavation\nunit",
             title = "Change over time in flake shape") +  #adjust accordingly)
             coord_fixed(ratio = 1)  + #adjustable for variation-weighted plots
             theme(panel.background = element_rect(fill='white',
                                        colour = "white"),
              plot.background = element_rect(fill='white',
                                       colour = "white")) +
    theme(plot.title = element_blank())
```

@@

```{r, fig.cap="PCA biplot for flake shape and mass cluster groups"}

@@

<!-- Below are my attempts to create a nice looking plot_grid of the three biplots. I was not able to get it to display properly, so I am just printing off each biplot individually all in a row as a temporary measure.  -->
```{r}
library(cowplot)

# plot_grid(
#  cortex_biplot, NULL, NULL,  excavation_unit_biplot,  mass_biplot, NULL,
#  ncol = 2,
#  labels = c("A", NULL, NULL,"B","C",NULL),
#  label_size = 12,
#  align = "v",
#  rel_heights = c(1.1,
#                  1,
#                  1.1,
#                  4,
#                  1,
#                  1),
#  rel_widths = c(2,
#                 2,
#                 2,
#                 4,
#                 2,
#                 1))

@@

```{r cortex-biplot, fig.cap="PCA biplot for flake shape and dorsal cortex class."}
cortex_biplot
```

```{r excavation-unit-biplot, fig.cap="PCA biplot for flake shape and excavation unit."}
excavation_unit_biplot
```

```{r mass-biplot, fig.cap="PCA biplot for flake shape and mass cluster groups"}
mass_biplot
```

In Figure \@ref(fig:mass-biplot) we see that greater shape variation is found in the lightest mass classes. The two lightest mass clusters, one and two, are in purple and blue respectively. These first two mass classes span the largest area on the biplot, signifying a larger degree of variation overall.
